### 2019-09-20 ch8_guidelines/content.tex
change to uk spelling

Many fields of computational research are characterized by a growing number of available methods for data analysis. For example, at the time of writing, almost 400 methods are available for analyzing data from single-cell RNA-sequencing experiments \cite{zappia_exploringsinglecellrnaseq_2018}. For experimental researchers and method users, this represents both an opportunity and a challenge, since method choice can significantly affect conclusions.

@@

Our aim is to complement previous reviews by providing a summary of essential guidelines for designing, performing, and interpreting benchmarks. While all guidelines are essential for a truly excellent benchmark, some are more fundamental than others. Our target audience consists of computational researchers who are interested in performing a benchmarking study, or who have already begun one. Our review spans the full pipeline of benchmarking, from defining the scope to best practices for reproducibility. This includes crucial questions regarding design and evaluation principles: for example, using rankings according to evaluation metrics to identify a set of high-performing methods, and then highlighting different strengths and tradeoffs among these.

@@

A neutral benchmark or community challenge should be as comprehensive as possible, although for any benchmark there will be tradeoffs in terms of available resources. To minimize perceived bias, a research group conducting a neutral benchmark should be approximately equally familiar with all included methods, reflecting typical usage of the methods by independent researchers \cite{boulesteix_pleaneutralcomparison_2013}. Alternatively, the group could include the original method authors, so that each method is evaluated under optimal conditions; methods whose authors decline to take part should be reported. In either case, bias due to focusing attention on particular methods should be avoided -- for example, when tuning parameters or fixing bugs. Strategies to avoid these types of biases, such as the use of blinding, have been previously proposed \cite{boulesteix_evidencebasedcomputationalstatistics_2017}.

@@

The selection of methods to include in the benchmark will be guided by the purpose and scope of the study. A neutral benchmark should include all available methods for a certain type of analysis. In this case, the publication describing the benchmark will also function as a review of the literature; a summary table describing the methods is a key output (e.g. Figure 2 in \cite{saelens_comparisonsinglecelltrajectory_2019} or Table 1 in \cite{weber_comparisonclusteringmethods_2016}). Alternatively, it may make sense to include only a subset of methods, by defining inclusion criteria: for example, all methods that (i) provide freely available software implementations, (ii) are available for commonly used operating systems, and (iii) can successfully be installed without errors following a reasonable amount of trouble-shooting. Such criteria should be chosen without favoring any methods, and exclusion of any widely used methods should be justified. A useful strategy can be to involve method authors within the process, since they may provide additional details on optimal usage. In addition, community involvement can lead to new collaborations and inspire future method development. However, the overall neutrality and balance of the resulting research team should be maintained. Finally, if the benchmark is organized as a community challenge, the selection of methods will be determined by the participants. In this case, it is important to communicate the initiative widely -- for example, through an established network such as DREAM challenges. However, some authors may choose not to participate; a summary table documenting non-included methods should be provided in this case.

@@

Simulated data have the advantage that a known true signal (or ground truth) can easily be introduced; for example, whether a gene is differentially expressed. Quantitative performance metrics measuring the ability to recover the known truth can then be calculated. However, it is important to demonstrate that simulations accurately reflect relevant properties of real data, by inspecting empirical summaries of both simulated and real datasets (e.g. using automated tools \cite{soneson_unifiedqualityverification_2018}). The set of empirical summaries to use is context-specific; for example, for single-cell RNA-sequencing, dropout profiles and dispersion-mean relationships should be compared \cite{soneson_biasrobustnessscalability_2018}; for DNA methylation, correlation patterns among neighboring CpG sites should be investigated \cite{korthauer_detectionaccuratefalse_2019}; for comparing mapping algorithms, error profiles of the sequencing platforms should be considered \cite{caboche_comparisonmappingalgorithms_2014}. Simplified simulations can also be useful, to evaluate a new method under a basic scenario, or to systematically test aspects such as scalability and stability. However, overly simplistic simulations should be avoided, since these will not provide useful information on performance. A further advantage of simulated data is that it is possible to generate as much data as required; for example, to study variability and draw statistically valid conclusions.

Experimental data often do not contain a ground truth, making it difficult to calculate performance metrics. Instead, methods may be evaluated by comparing them against each other (e.g. overlap between sets of detected differential features \cite{nowicka_drimseqdirichletmultinomialframework_2016}), or against a current widely accepted method or gold standard (e.g. manual gating to define cell populations in high-dimensional cytometry \cite{weber_comparisonclusteringmethods_2016, aghaeepour_criticalassessmentautomated_2013}, or fluorescence in situ hybridization to validate absolute copy number predictions \cite{zheng_benchmarkingcontextsdetails_2017}). In the context of supervised learning, the response variable to be predicted is known in the manually labeled training and test data. However, individual datasets should not be overused, and using the same dataset for both method development and evaluation should be avoided, due to the risk of overfitting and overly optimistic results \cite{grimm_evaluationtoolsused_2015,jelizarow_overoptimismbioinformaticsillustration_2010}. In some cases, it is also possible to design experimental datasets containing a ground truth. Examples include: (i) spiking in synthetic RNA molecules at known relative concentrations \cite{jiang_syntheticspikeinstandards_2011} in RNA-sequencing experiments (e.g. \cite{seqc_comprehensiveassessmentrnaseq_2014,garalde_highlyparalleldirect_2018}), (ii) large-scale validation of gene expression measurements by quantitative polymerase chain reaction (e.g. \cite{seqc_comprehensiveassessmentrnaseq_2014}), (iii) using genes located on sex chromosomes as a proxy for silencing of DNA methylation status (e.g. \cite{law_voomprecisionweights_2014,fang_genomiclandscapehuman_2012}), (iv) using fluorescence-activated cell sorting to sort cells into known subpopulations prior to single-cell RNA-sequencing (e.g. \cite{soneson_biasrobustnessscalability_2018, schaum_singlecelltranscriptomics20_2018, zheng_massivelyparalleldigital_2017}), or (v) mixing different cell lines to create pseudo-cells \cite{tian_benchmarkingsinglecell_2019}. However, it may be difficult to ensure that the ground truth represents an appropriate level of variability -- for example, the variability of spiked-in material, or whether method performance on cell line data is relevant to outbred populations. Alternatively, experimental datasets may be evaluated qualitatively, for example, by judging whether each method can recover previous discoveries, although this strategy relies on the validity of previous results.

A further technique is to design semi-simulated datasets that combine real experimental data with an in silico (i.e., computational) spike-in signal; for example, by combining cells or genes from null (e.g. healthy) samples with a subset of cells or genes from samples expected to contain a true differential signal (examples include \cite{weber_diffcytdifferentialdiscovery_2019,arvaniti_sensitivedetectionrare_2017,rigaill_syntheticdatasets_2018}). This strategy can create datasets with more realistic levels of variability and correlation, together with a ground truth.

Overall, there is no perfect reference dataset, and the selection of appropriate datasets will involve tradeoffs, for example, regarding the level of complexity. Both simulated and experimental data should not be too simple (e.g. two of the datasets in the FlowCAP-II challenge \cite{aghaeepour_criticalassessmentautomated_2013} gave perfect performance for several algorithms) or too difficult (e.g. for the third dataset in FlowCAP-II, no algorithms performed well); in these situations, it can be impossible to distinguish performance. In some cases, individual datasets have also been found to be unrepresentative, leading to over-optimistic or otherwise biased assessment of methods (e.g. \cite{lowes_bralibasedentatale_2017}). Overall, the key to truly excellent benchmarking is diversity of evaluations, i.e., using a range of metrics and datasets that span the range of those that might be encountered in practice, so that performance estimates can be credibly extrapolated.

@@

Parameter settings can have a crucial impact on performance. Some methods have a large number of parameters, and tuning parameters to optimal values can require significant effort and expertise. For a neutral benchmark, a range of parameter values should ideally be considered for each method, although tradeoffs need to be considered regarding available time and computational resources. Importantly, the selection of parameter values should comply with the neutrality principle, i.e., certain methods should not be favored over others through more extensive parameter tuning.

There are three major strategies for choosing parameters. The first (and simplest) is to use default values for all parameters. Default parameters may be adequate for many methods, although this is difficult to judge in advance. While this strategy may be viewed as too simplistic for some neutral benchmarks, it reflects typical usage. We used default parameters in several neutral benchmarks where we were interested in performance for untrained users \cite{saelens_comparisonsinglecelltrajectory_2019,couronne_randomforestlogistic_2018,schneider_mortalityriskacute_2016}. In addition, for \cite{saelens_comparisonsinglecelltrajectory_2019}, due to the large number of methods and datasets, total runtime was already around a week using 192 processor cores, necessitating judgment in the scope of parameter tuning. The second strategy is to choose parameters based on previous experience or published values. This relies on familiarity with the methods and the literature, reflecting usage by expert users. The third strategy is to use a systematic or automated parameter tuning procedure -- for example, a grid search across ranges of values for multiple parameters or techniques such as cross-validation (e.g. \cite{saelens_comprehensiveevaluationmodule_2018}). The strategies may also be combined, for example, by setting non-critical parameters to default values and performing a grid search for key parameters. Regardless, neutrality should be maintained: comparing methods with the same strategy makes sense, while comparing one method with default parameters against another with extensive tuning makes for an unfair comparison.

@@

Evaluation of methods will rely on one or more quantitative performance metrics (Figure  \ref{fig:fig2_metrics}A). The choice of metric depends on the type of method and data. For example, for classification tasks with a ground truth, metrics include the true positive rate (TPR; sensitivity or recall), false positive rate (FPR; 1 - specificity), and false discovery rate (FDR). For clustering tasks, common metrics include the F1 score, adjusted Rand index, normalized mutual information, precision, and recall; some of these can be calculated at the cluster level as well as averaged (and optionally weighted) across clusters (e.g. these metrics were used to evaluate clustering methods in our own work \cite{duo_systematicperformanceevaluation_2018,weber_comparisonclusteringmethods_2016}  and by others \cite{freytag_comparisonclusteringtools_2018,aghaeepour_criticalassessmentautomated_2013,wiwie_comparingperformancebiomedical_2015}). Several of these metrics can also be compared visually to capture the tradeoff between sensitivity and specificity, for example, using receiver operating characteristic (ROC) curves (TPR versus FPR), TPR versus FDR curves, or precision-recall (PR) curves (Figure \ref{fig:fig2_metrics}B). For imbalanced datasets, PR curves have been shown to be more informative than ROC curves \cite{saito_precisionrecallplotmore_2015,powers_visualizationtradeoffevaluation_2015}. These visual metrics can also be summarized as a single number, such as area under the ROC or PR curve; examples from our work include \cite{weber_diffcytdifferentialdiscovery_2019,soneson_biasrobustnessscalability_2018}. In addition to the tradeoff between sensitivity and specificity, a methods operating point' is important; in particular, whether the threshold used (e.g. 5\% FDR) is calibrated to achieve the specified error rate. We often overlay this onto TPR-FDR curves by filled or open circles (e.g. Figure \ref{fig:fig2_metrics}B, generated using the iCOBRA package \cite{soneson_icobraopenreproducible_2016}); examples from our work include \cite{weber_diffcytdifferentialdiscovery_2019,nowicka_drimseqdirichletmultinomialframework_2016,zhou_robustlydetectingdifferential_2014,soneson_differentialanalysesrnaseq_2016}.

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\hugefigure]{fig/essential_guidelines_figure2} 
	\caption{\textbf{Summary and examples of performance metrics.} \textbf{A:} Schematic overview of classes of frequently used performance metrics, including examples (\textit{boxes outlined in gray}). \textbf{B:} Examples of popular visualizations of quantitative performance metrics for classification methods, using reference datasets with a ground truth. ROC curves (\textit{left}). TPR versus FDR curves (\textit{center}); circles represent observed TPR and FDR at typical FDR thresholds of 1, 5, and 10\%, with filled circles indicating observed FDR lower than or equal to the imposed threshold. PR curves (\textit{right}). Visualizations were generated using iCOBRA R/Bioconductor package \cite{soneson_icobraopenreproducible_2016}. \textit{FDR} false discovery rate, \textit{FPR} false positive rate, \textit{PR} precision-recall, \textit{ROC} receiver operating characteristic, \textit{TPR} true positive rate}
	\label{fig:fig2_metrics}
\end{figure}

@@

Additional metrics that do not rely on a ground truth include measures of stability, stochasticity, and robustness. These measures may be quantified by running methods multiple times using different inputs or subsampled data (e.g. we observed substantial variability in performance for some methods in \cite{soneson_biasrobustnessscalability_2018,weber_comparisonclusteringmethods_2016}). Missing values may occur if a method does not return any values for a certain metric, for example, due to a failure to converge or other computational issues such as excessive runtime or memory requirements (e.g. \cite{saelens_comparisonsinglecelltrajectory_2019, soneson_biasrobustnessscalability_2018,weber_comparisonclusteringmethods_2016}). Fallback solutions such as imputation may be considered in this case \cite{bischl_benchmarkinglocalclassification_2013}, although these should be transparently reported. For non-deterministic methods (e.g. with random starts or stochastic optimization), variability in performance when using different random seeds or subsampled data should be characterized. Null comparisons can be constructed by randomizing group labels such that datasets do not contain any true signal, which can provide information on error rates (e.g. \cite{weber_diffcytdifferentialdiscovery_2019,zhou_robustlydetectingdifferential_2014,law_voomprecisionweights_2014}). However, these must be designed carefully to avoid confounding by batch or population structure, and to avoid strong within-group batch effects that are not accounted for.

For most benchmarks, multiple metrics will be relevant. Focusing on a single metric can give an incomplete view: methods may not be directly comparable if they are designed for different tasks, and different users may be interested in different aspects of performance. Therefore, a crucial design decision is whether to focus on an overall ranking, for example, by combining or weighting multiple metrics. In general, it is unlikely that a single method will perform best across all metrics, and performance differences between top-ranked methods for individual metrics can be small. Therefore, a good strategy is to use rankings from multiple metrics to identify a set of consistently high-performing methods, and then highlight the different strengths of these methods. For example, in \cite{weber_comparisonclusteringmethods_2016}, we identified methods that gave good clustering performance, and then highlighted differences in runtimes among these. In several studies, we have presented results in the form of a graphical summary of performance according to multiple criteria (examples include Figure 3 in \cite{saelens_comparisonsinglecelltrajectory_2019} and Figure 5 in \cite{soneson_biasrobustnessscalability_2018} from our work; and Figure 2 in \cite{sage_quantitativeevaluationsoftware_2015} and Figure 6 in \cite{korthauer_practicalguidemethods_2019} from other authors). Identifying methods that consistently underperform can also be useful, to allow readers to avoid these.

@@

In addition to the key quantitative performance metrics, methods should also be evaluated according to secondary measures, including runtime, scalability, and other computational requirements, as well as qualitative aspects such as user-friendliness, installation procedures, code quality, and documentation quality (Figure \ref{fig:fig2_metrics}A). From the user perspective, the final choice of method may involve tradeoffs according to these measures: an adequately performing method may be preferable to a top-performing method that is especially difficult to use.

In our experience, runtimes and scalability can vary enormously between methods (e.g. in our work, runtimes for cytometry clustering algorithms \cite{weber_comparisonclusteringmethods_2016} and metagenome analysis tools \cite{lindgreen_evaluationaccuracyspeed_2016} ranged across multiple orders of magnitude for the same datasets). Similarly, memory and other computational requirements can vary widely. Runtimes and scalability may be investigated systematically, for example, by varying the number of cells or genes in a single-cell RNA-sequencing dataset \cite{duo_systematicperformanceevaluation_2018,soneson_biasrobustnessscalability_2018}. In many cases, there is a tradeoff between performance and computational requirements. In practice, if computational requirements for a top-performing method are prohibitive, then a different method may be preferred by some users.

@@

For a truly excellent benchmark, results must be clearly interpreted from the perspective of the intended audience. For method users, results should be summarized in the form of recommendations. An overall ranking of methods (or separate rankings for multiple evaluation criteria) can provide a useful overview. However, as mentioned above, some methods may not be directly comparable (e.g. since they are designed for different tasks), and different users may be interested in different aspects of performance. In addition, it is unlikely that there will be a clear winner across all criteria, and performance differences between top-ranked methods can be small. Therefore, an informative strategy is to use the rankings to identify a set of high-performing methods, and to highlight the different strengths and tradeoffs among these methods. The interpretation may also involve biological or other domain knowledge to establish the scientific relevance of differences in performance. Importantly, neutrality principles should be preserved during the interpretation.

@@

For extensive benchmarks, online resources enable readers to interactively explore the results (examples from our work include \cite{saelens_comparisonsinglecelltrajectory_2019, weber_comparisonclusteringmethods_2016}, which allow users to filter metrics and datasets). Figure 3 displays an example of an interactive website from one of our benchmarks \cite{saelens_comparisonsinglecelltrajectory_2019}, which facilitates exploration of results and assists users with choosing a suitable method. While tradeoffs should be considered in terms of the amount of work required, these efforts are likely to have significant benefit for the community.

@@

In most cases, results will be published in a peer-reviewed article. For a neutral benchmark, the benchmark will be the main focus of the paper. For a benchmark to introduce a new method, the results will form one part of the exposition. We highly recommend publishing a preprint prior to peer review (e.g. on bioRxiv or arXiv) to speed up distribution of results, broaden accessibility, and solicit additional feedback. In particular, direct consultation with method authors can generate highly useful feedback (examples from our work are described in the acknowledgments in \cite{lindgreen_evaluationaccuracyspeed_2016,freyhult_exploringgenomicdark_2007}). Finally, at publication time, considering open access options will further broaden accessibility.

@@

\section{Discussion}
In this review, we have described a set of key principles for designing a high-quality computational benchmark. In our view, elements of all of these principles are essential. However, we have also emphasized that any benchmark will involve tradeoffs, due to limited expertise and resources, and that some principles are less central to the evaluation. Table \ref{tab:essential_principles} provides a summary of examples of key tradeoffs and pitfalls related to benchmarking, along with our judgment of how truly essential each principle is.

>>>>

Many fields of computational research are characterized by a growing number of available methods for data analysis. For example, at the time of writing, almost 400 methods are available for analysing data from single-cell RNA-sequencing experiments \cite{zappia_exploringsinglecellrnaseq_2018}. For experimental researchers and method users, this represents both an opportunity and a challenge, since method choice can significantly affect conclusions.

@@

Our aim is to complement previous reviews by providing a summary of essential guidelines for designing, performing, and interpreting benchmarks. While all guidelines are essential for a truly excellent benchmark, some are more fundamental than others. Our target audience consists of computational researchers who are interested in performing a benchmarking study, or who have already begun one. Our review spans the full pipeline of benchmarking, from defining the scope to best practices for reproducibility. This includes crucial questions regarding design and evaluation principles: for example, using rankings according to evaluation metrics to identify a set of high-performing methods, and then highlighting different strengths and trade-offs among these.

@@

A neutral benchmark or community challenge should be as comprehensive as possible, although for any benchmark there will be trade-offs in terms of available resources. To minimize perceived bias, a research group conducting a neutral benchmark should be approximately equally familiar with all included methods, reflecting typical usage of the methods by independent researchers \cite{boulesteix_pleaneutralcomparison_2013}. Alternatively, the group could include the original method authors, so that each method is evaluated under optimal conditions; methods whose authors decline to take part should be reported. In either case, bias due to focusing attention on particular methods should be avoided -- for example, when tuning parameters or fixing bugs. Strategies to avoid these types of biases, such as the use of blinding, have been previously proposed \cite{boulesteix_evidencebasedcomputationalstatistics_2017}.

@@

The selection of methods to include in the benchmark will be guided by the purpose and scope of the study. A neutral benchmark should include all available methods for a certain type of analysis. In this case, the publication describing the benchmark will also function as a review of the literature; a summary table describing the methods is a key output (e.g. Figure 2 in \cite{saelens_comparisonsinglecelltrajectory_2019} or Table 1 in \cite{weber_comparisonclusteringmethods_2016}). Alternatively, it may make sense to include only a subset of methods, by defining inclusion criteria: for example, all methods that (i) provide freely available software implementations, (ii) are available for commonly used operating systems, and (iii) can successfully be installed without errors following a reasonable amount of trouble-shooting. Such criteria should be chosen without favouring any methods, and exclusion of any widely used methods should be justified. A useful strategy can be to involve method authors within the process, since they may provide additional details on optimal usage. In addition, community involvement can lead to new collaborations and inspire future method development. However, the overall neutrality and balance of the resulting research team should be maintained. Finally, if the benchmark is organized as a community challenge, the selection of methods will be determined by the participants. In this case, it is important to communicate the initiative widely -- for example, through an established network such as DREAM challenges. However, some authors may choose not to participate; a summary table documenting non-included methods should be provided in this case.

@@

Simulated data have the advantage that a known true signal (or ground truth) can easily be introduced; for example, whether a gene is differentially expressed. Quantitative performance metrics measuring the ability to recover the known truth can then be calculated. However, it is important to demonstrate that simulations accurately reflect relevant properties of real data, by inspecting empirical summaries of both simulated and real datasets (e.g. using automated tools \cite{soneson_unifiedqualityverification_2018}). The set of empirical summaries to use is context-specific; for example, for single-cell RNA-sequencing, drop-out profiles and dispersion-mean relationships should be compared \cite{soneson_biasrobustnessscalability_2018}; for DNA methylation, correlation patterns among neighbouring CpG sites should be investigated \cite{korthauer_detectionaccuratefalse_2019}; for comparing mapping algorithms, error profiles of the sequencing platforms should be considered \cite{caboche_comparisonmappingalgorithms_2014}. Simplified simulations can also be useful, to evaluate a new method under a basic scenario, or to systematically test aspects such as scalability and stability. However, overly simplistic simulations should be avoided, since these will not provide useful information on performance. A further advantage of simulated data is that it is possible to generate as much data as required; for example, to study variability and draw statistically valid conclusions.

Experimental data often do not contain a ground truth, making it difficult to calculate performance metrics. Instead, methods may be evaluated by comparing them against each other (e.g. overlap between sets of detected differential features \cite{nowicka_drimseqdirichletmultinomialframework_2016}), or against a current widely accepted method or gold standard (e.g. manual gating to define cell populations in high-dimensional cytometry \cite{weber_comparisonclusteringmethods_2016, aghaeepour_criticalassessmentautomated_2013}, or fluorescence \textit{in situ} hybridization to validate absolute copy number predictions \cite{zheng_benchmarkingcontextsdetails_2017}). In the context of supervised learning, the response variable to be predicted is known in the manually labelled training and test data. However, individual datasets should not be overused, and using the same dataset for both method development and evaluation should be avoided, due to the risk of overfitting and overly optimistic results \cite{grimm_evaluationtoolsused_2015,jelizarow_overoptimismbioinformaticsillustration_2010}. In some cases, it is also possible to design experimental datasets containing a ground truth. Examples include: (i) spiking in synthetic RNA molecules at known relative concentrations \cite{jiang_syntheticspikeinstandards_2011} in RNA-sequencing experiments (e.g. \cite{seqc_comprehensiveassessmentrnaseq_2014,garalde_highlyparalleldirect_2018}), (ii) large-scale validation of gene expression measurements by quantitative polymerase chain reaction (e.g. \cite{seqc_comprehensiveassessmentrnaseq_2014}), (iii) using genes located on sex chromosomes as a proxy for silencing of DNA methylation status (e.g. \cite{law_voomprecisionweights_2014,fang_genomiclandscapehuman_2012}), (iv) using fluorescence-activated cell sorting to sort cells into known sub-populations prior to single-cell RNA-sequencing (e.g. \cite{soneson_biasrobustnessscalability_2018, schaum_singlecelltranscriptomics20_2018, zheng_massivelyparalleldigital_2017}), or (v) mixing different cell lines to create pseudo-cells \cite{tian_benchmarkingsinglecell_2019}. However, it may be difficult to ensure that the ground truth represents an appropriate level of variability -- for example, the variability of spiked-in material, or whether method performance on cell line data is relevant to out-bred populations. Alternatively, experimental datasets may be evaluated qualitatively, for example, by judging whether each method can recover previous discoveries, although this strategy relies on the validity of previous results.

A further technique is to design semi-simulated datasets that combine real experimental data with an \textit{in silico} (i.e., computational) spike-in signal; for example, by combining cells or genes from null (e.g. healthy) samples with a subset of cells or genes from samples expected to contain a true differential signal (examples include \cite{weber_diffcytdifferentialdiscovery_2019,arvaniti_sensitivedetectionrare_2017,rigaill_syntheticdatasets_2018}). This strategy can create datasets with more realistic levels of variability and correlation, together with a ground truth.

Overall, there is no perfect reference dataset, and the selection of appropriate datasets will involve trade-offs, for example, regarding the level of complexity. Both simulated and experimental data should not be too simple (e.g. two of the datasets in the FlowCAP-II challenge \cite{aghaeepour_criticalassessmentautomated_2013} gave perfect performance for several algorithms) or too difficult (e.g. for the third dataset in FlowCAP-II, no algorithms performed well); in these situations, it can be impossible to distinguish performance. In some cases, individual datasets have also been found to be unrepresentative, leading to over-optimistic or otherwise biased assessment of methods (e.g. \cite{lowes_bralibasedentatale_2017}). Overall, the key to truly excellent benchmarking is diversity of evaluations, i.e., using a range of metrics and datasets that span the range of those that might be encountered in practice, so that performance estimates can be credibly extrapolated.

@@

Parameter settings can have a crucial impact on performance. Some methods have a large number of parameters, and tuning parameters to optimal values can require significant effort and expertise. For a neutral benchmark, a range of parameter values should ideally be considered for each method, although trade-offs need to be considered regarding available time and computational resources. Importantly, the selection of parameter values should comply with the neutrality principle, i.e., certain methods should not be favoured over others through more extensive parameter tuning.

There are three major strategies for choosing parameters. The first (and simplest) is to use default values for all parameters. Default parameters may be adequate for many methods, although this is difficult to judge in advance. While this strategy may be viewed as too simplistic for some neutral benchmarks, it reflects typical usage. We used default parameters in several neutral benchmarks where we were interested in performance for untrained users \cite{saelens_comparisonsinglecelltrajectory_2019,couronne_randomforestlogistic_2018,schneider_mortalityriskacute_2016}. In addition, for \cite{saelens_comparisonsinglecelltrajectory_2019}, due to the large number of methods and datasets, total runtime was already around a week using 192 processor cores, necessitating judgement in the scope of parameter tuning. The second strategy is to choose parameters based on previous experience or published values. This relies on familiarity with the methods and the literature, reflecting usage by expert users. The third strategy is to use a systematic or automated parameter tuning procedure -- for example, a grid search across ranges of values for multiple parameters or techniques such as cross-validation (e.g. \cite{saelens_comprehensiveevaluationmodule_2018}). The strategies may also be combined, for example, by setting non-critical parameters to default values and performing a grid search for key parameters. Regardless, neutrality should be maintained: comparing methods with the same strategy makes sense, while comparing one method with default parameters against another with extensive tuning makes for an unfair comparison.

@@

Evaluation of methods will rely on one or more quantitative performance metrics (Figure  \ref{fig:fig2_metrics}A). The choice of metric depends on the type of method and data. For example, for classification tasks with a ground truth, metrics include the true positive rate (TPR; sensitivity or recall), false positive rate (FPR; 1 - specificity), and false discovery rate (FDR). For clustering tasks, common metrics include the F1 score, adjusted Rand index, normalized mutual information, precision, and recall; some of these can be calculated at the cluster level as well as averaged (and optionally weighted) across clusters (e.g. these metrics were used to evaluate clustering methods in our own work \cite{duo_systematicperformanceevaluation_2018,weber_comparisonclusteringmethods_2016}  and by others \cite{freytag_comparisonclusteringtools_2018,aghaeepour_criticalassessmentautomated_2013,wiwie_comparingperformancebiomedical_2015}). Several of these metrics can also be compared visually to capture the trade-off between sensitivity and specificity, for example, using receiver operating characteristic (ROC) curves (TPR versus FPR), TPR versus FDR curves, or precision-recall (PR) curves (Figure \ref{fig:fig2_metrics}B). For imbalanced datasets, PR curves have been shown to be more informative than ROC curves \cite{saito_precisionrecallplotmore_2015,powers_visualizationtradeoffevaluation_2015}. These visual metrics can also be summarized as a single number, such as area under the ROC or PR curve; examples from our work include \cite{weber_diffcytdifferentialdiscovery_2019,soneson_biasrobustnessscalability_2018}. In addition to the trade-off between sensitivity and specificity, a methods operating point' is important; in particular, whether the threshold used (e.g. 5\% FDR) is calibrated to achieve the specified error rate. We often overlay this onto TPR-FDR curves by filled or open circles (e.g. Figure \ref{fig:fig2_metrics}B, generated using the iCOBRA package \cite{soneson_icobraopenreproducible_2016}); examples from our work include \cite{weber_diffcytdifferentialdiscovery_2019,nowicka_drimseqdirichletmultinomialframework_2016,zhou_robustlydetectingdifferential_2014,soneson_differentialanalysesrnaseq_2016}.

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\hugefigure]{fig/essential_guidelines_figure2} 
	\caption{\textbf{Summary and examples of performance metrics.} \textbf{A:} Schematic overview of classes of frequently used performance metrics, including examples (\textit{boxes outlined in gray}). \textbf{B:} Examples of popular visualizations of quantitative performance metrics for classification methods, using reference datasets with a ground truth. ROC curves (\textit{left}). TPR versus FDR curves (\textit{centre}); circles represent observed TPR and FDR at typical FDR thresholds of 1, 5, and 10\%, with filled circles indicating observed FDR lower than or equal to the imposed threshold. PR curves (\textit{right}). Visualizations were generated using iCOBRA R/Bioconductor package \cite{soneson_icobraopenreproducible_2016}. \textit{FDR} false discovery rate, \textit{FPR} false positive rate, \textit{PR} precision-recall, \textit{ROC} receiver operating characteristic, \textit{TPR} true positive rate}
	\label{fig:fig2_metrics}
\end{figure}

@@

Additional metrics that do not rely on a ground truth include measures of stability, stochasticity, and robustness. These measures may be quantified by running methods multiple times using different inputs or sub-sampled data (e.g. we observed substantial variability in performance for some methods in \cite{soneson_biasrobustnessscalability_2018,weber_comparisonclusteringmethods_2016}). Missing values may occur if a method does not return any values for a certain metric, for example, due to a failure to converge or other computational issues such as excessive runtime or memory requirements (e.g. \cite{saelens_comparisonsinglecelltrajectory_2019, soneson_biasrobustnessscalability_2018,weber_comparisonclusteringmethods_2016}). Fall-back solutions such as imputation may be considered in this case \cite{bischl_benchmarkinglocalclassification_2013}, although these should be transparently reported. For non-deterministic methods (e.g. with random starts or stochastic optimization), variability in performance when using different random seeds or sub-sampled data should be characterized. Null comparisons can be constructed by randomizing group labels such that datasets do not contain any true signal, which can provide information on error rates (e.g. \cite{weber_diffcytdifferentialdiscovery_2019,zhou_robustlydetectingdifferential_2014,law_voomprecisionweights_2014}). However, these must be designed carefully to avoid confounding by batch or population structure, and to avoid strong within-group batch effects that are not accounted for.

For most benchmarks, multiple metrics will be relevant. Focusing on a single metric can give an incomplete view: methods may not be directly comparable if they are designed for different tasks, and different users may be interested in different aspects of performance. Therefore, a crucial design decision is whether to focus on an overall ranking, for example, by combining or weighting multiple metrics. In general, it is unlikely that a single method will perform best across all metrics, and performance differences between top-ranked methods for individual metrics can be small. Therefore, a good strategy is to use rankings from multiple metrics to identify a set of consistently high-performing methods, and then highlight the different strengths of these methods. For example, in \cite{weber_comparisonclusteringmethods_2016}, we identified methods that gave good clustering performance, and then highlighted differences in run-times among these. In several studies, we have presented results in the form of a graphical summary of performance according to multiple criteria (examples include Figure 3 in \cite{saelens_comparisonsinglecelltrajectory_2019} and Figure 5 in \cite{soneson_biasrobustnessscalability_2018} from our work; and Figure 2 in \cite{sage_quantitativeevaluationsoftware_2015} and Figure 6 in \cite{korthauer_practicalguidemethods_2019} from other authors). Identifying methods that consistently under-perform can also be useful, to allow readers to avoid these.

@@

In addition to the key quantitative performance metrics, methods should also be evaluated according to secondary measures, including runtime, scalability, and other computational requirements, as well as qualitative aspects such as user-friendliness, installation procedures, code quality, and documentation quality (Figure \ref{fig:fig2_metrics}A). From the user perspective, the final choice of method may involve trade-offs according to these measures: an adequately performing method may be preferable to a top-performing method that is especially difficult to use.

In our experience, run-times and scalability can vary enormously between methods (e.g. in our work, run-times for cytometry clustering algorithms \cite{weber_comparisonclusteringmethods_2016} and meta-genome analysis tools \cite{lindgreen_evaluationaccuracyspeed_2016} ranged across multiple orders of magnitude for the same datasets). Similarly, memory and other computational requirements can vary widely. Run-times and scalability may be investigated systematically, for example, by varying the number of cells or genes in a single-cell RNA-sequencing dataset \cite{duo_systematicperformanceevaluation_2018,soneson_biasrobustnessscalability_2018}. In many cases, there is a trade-off between performance and computational requirements. In practice, if computational requirements for a top-performing method are prohibitive, then a different method may be preferred by some users.

@@

For a truly excellent benchmark, results must be clearly interpreted from the perspective of the intended audience. For method users, results should be summarized in the form of recommendations. An overall ranking of methods (or separate rankings for multiple evaluation criteria) can provide a useful overview. However, as mentioned above, some methods may not be directly comparable (e.g. since they are designed for different tasks), and different users may be interested in different aspects of performance. In addition, it is unlikely that there will be a clear winner across all criteria, and performance differences between top-ranked methods can be small. Therefore, an informative strategy is to use the rankings to identify a set of high-performing methods, and to highlight the different strengths and trade-offs among these methods. The interpretation may also involve biological or other domain knowledge to establish the scientific relevance of differences in performance. Importantly, neutrality principles should be preserved during the interpretation.

@@

For extensive benchmarks, online resources enable readers to interactively explore the results (examples from our work include \cite{saelens_comparisonsinglecelltrajectory_2019, weber_comparisonclusteringmethods_2016}, which allow users to filter metrics and datasets). Figure 3 displays an example of an interactive website from one of our benchmarks \cite{saelens_comparisonsinglecelltrajectory_2019}, which facilitates exploration of results and assists users with choosing a suitable method. While trade-offs should be considered in terms of the amount of work required, these efforts are likely to have significant benefit for the community.

@@

In most cases, results will be published in a peer-reviewed article. For a neutral benchmark, the benchmark will be the main focus of the paper. For a benchmark to introduce a new method, the results will form one part of the exposition. We highly recommend publishing a preprint prior to peer review (e.g. on bioRxiv or arXiv) to speed up distribution of results, broaden accessibility, and solicit additional feedback. In particular, direct consultation with method authors can generate highly useful feedback (examples from our work are described in the acknowledgements in \cite{lindgreen_evaluationaccuracyspeed_2016,freyhult_exploringgenomicdark_2007}). Finally, at publication time, considering open access options will further broaden accessibility.

@@

\section{Discussion}
In this review, we have described a set of key principles for designing a high-quality computational benchmark. In our view, elements of all of these principles are essential. However, we have also emphasized that any benchmark will involve trade-offs, due to limited expertise and resources, and that some principles are less central to the evaluation. Table \ref{tab:essential_principles} provides a summary of examples of key trade-offs and pitfalls related to benchmarking, along with our judgement of how truly essential each principle is.
